Raw img Data

### 2021-06-07 R/Raw Img Data.Rmd
changed folder and got aggregates files import

---
title: "AggregateCounts"
author: "Juan P Barraza"
date: "6/4/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
filter <- dplyr::filter

conditionlist= list('wt','pqsL', 'phz', 'mono')

ReadAggregateFile(fileList[1], "Pa", "1", "wt")
GetAggregates()

datos <-read.csv(fileList[1], header = F)
colnames(datos)<-c('Size')
datos1<-datos %>% filter(!Size<0.5) #first filter the size

ReadAggregateFile<-function(file, species, timepoint, condition){#make a dataframe of the aggregate size list and add experimental parameters
  datos <-read.csv(file, header = F)
  colnames(datos)<-c('Size')
  datos<-datos %>% filter(!Size<0.5) #first filter the size
  datos<-datos %>% mutate(Species = species)#add parameters
  datos<-datos %>% mutate(TimePoint = timepoint)
  datos<-datos %>% mutate(Condition = condition)
  return(datos)
}

GetAggregates<-function(){#import all experiments at once
  folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (condition in 1:length(conditionlist)){
    currentCondition<-fileList[grep(conditionlist[condition],fileList)] #find files for each condition
    print(currentCondition)
    for (species in 1:3){
      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
      print(currentTimePoint)
      #growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
    }
  }
  return(growthDf)
}

for (i in 0:3){
  print(i)
  }

>>>>

---
title: "Raw img Data"
author: "Juan P Barraza"
date: "4/23/2021"
output: html_document
---

```{r setup, include=FALSE}

#####
imgHisData<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Images data/Image histogram data/cowtd1m2p2a_1.csv",header = F)
NewNames <- c('zeroInt','zeroPercent','maxInt','firstZero','totalZeroes','level','calculatedG2','tailBins', 'numtailEnd','optimalG','meanIntensity','sdIntensity')
names(imgHisData) <- NewNames
